### 2022-04-08 manuscript.tex
Update 06.future.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/7a02dfb8a9274d8e9859aa2cf500dd7720d847a5.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/7a02dfb8a9274d8e9859aa2cf500dd7720d847a5/checks
https://github.com/scherzerthesis/thesis/actions/runs/2117218579

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/e0977775368cdf68ea6d2822abaadc5364aa0e6b/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/e0977775368cdf68ea6d2822abaadc5364aa0e6b}{scherzerthesis/thesis@e097777}
on April 8, 2022.

@@

Every year in the United States, approximately 4000 patients succumb to \emph{BRAF}-mutant lung cancer. Unlike melanoma or thyroid cancer, \emph{BRAF\textsuperscript{V600E}} is not the most common \emph{BRAF} alteration. Less potent MAPK activating mutations such as \emph{BRAF\^{}G469A} are more common(Bracht et al., 2019; \textbf{omid:30770389?}). It is likely that less potent MAPK activators serve as support signaling molecules for oncogenes like \emph{KRAS(G12D)}, which fine-tune pathway activation. However, little is known about how vital non-V600E \emph{BRAF} mutations are in the evolution of lung adenocarcinoma. Therefore, preclinical models such as genetically engineered mice will be vital to determine the role of non-\emph{BRAF\textsuperscript{V600E}} mutations in lung adenocarcinoma. Previous work from our lab has established that \emph{BRAF\textsuperscript{V600E}} plays a substantial role in the early formation of lung benign lung tumors but fails to form lung adenocarcinoma. Rather, benign to malignant lung cancer progression depends on additional genetic alterations(Trejo et al., 2013).

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/7a02dfb8a9274d8e9859aa2cf500dd7720d847a5/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/7a02dfb8a9274d8e9859aa2cf500dd7720d847a5}{scherzerthesis/thesis@7a02dfb}
on April 8, 2022.

@@

Every year in the United States, approximately 4000 patients succumb to \emph{BRAF}-mutant lung cancer. Unlike melanoma or thyroid cancer, \emph{BRAF\textsuperscript{V600E}} is not the most common \emph{BRAF} alteration. Less potent MAPK activating mutations such as \emph{BRAF\textsuperscript{G469A}} are more common(Bracht et al., 2019; Yaeger and Corcoran, 2019). It is likely that less potent MAPK activators serve as support signaling molecules for oncogenes like \emph{KRAS(G12D)}, which fine-tune pathway activation. However, little is known about how vital non-V600E \emph{BRAF} mutations are in the evolution of lung adenocarcinoma. Therefore, preclinical models such as genetically engineered mice will be vital to determine the role of non-\emph{BRAF\textsuperscript{V600E}} mutations in lung adenocarcinoma. Previous work from our lab has established that \emph{BRAF\textsuperscript{V600E}} plays a substantial role in the early formation of lung benign lung tumors but fails to form lung adenocarcinoma. Rather, benign to malignant lung cancer progression depends on additional genetic alterations(Trejo et al., 2013).

@@

\leavevmode\vadjust pre{\hypertarget{ref-NqyqCnIL}{}}%
Yaeger, R., and Corcoran, R.B. (2019). Targeting Alterations in the RAF-MEK Pathway. Cancer Discov \emph{9}, 329--341. \url{https://doi.org/10.1158/2159-8290.cd-18-1321}.
